Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-21 doc/PRF2022/PRF_main.tex
yny

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f), the relative enclosed area $A/A_0$
  calculated from the bilayer midplane decreases over time. The inset
  shows the relative length $L/L_0$ which remains nearly constant with a
  small oscillation. The inset and main panel have the same horizontal
  axis.} 
  \todo[inline]{We propose to relate panel (f) to the pressure drops
  across the JP vesicles. Also, panel (a) should be its own figure, and
  (b)--(e) can be their own figure, but with darker stream lines. Also,
  should not be talking about tank treading, but rather about sliding
  between layers, and how they are affected by the correlation between
  the bilayer location and the TG cell boundary. This correlation also
  somehow determines the shape. Can count the number of partial TG cells
  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
  (e) has 1 cell.}
\end{figure}

@@

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
all cases, the vesicle and TG flow reach a steady-state tank-treading
motion \todo[inline]{no longer true}, but the geometry and motion varies
non-monotonically. For $\lambda$ ranging from $1$ nm to $4$ nm, the
steady-state vesicle shape goes from an octagon, to a dimpled square, to
a rounded diamond, to a rounded square. Surprisingly, the direction of
rotation switches: for $\lambda = 2$ nm the rotation is clockwise, while
for $\lambda = 4$ nm the rotation is counterclockwise. Finally, we
calculate the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
steady-state that is greatest for $\lambda = 4$ nm yet least for
$\lambda = 2$ nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
words, the flow pattern is non-monotonic in the cell size $\lambda$.

>>>>

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f), the relative enclosed area $A/A_0$
  calculated from the bilayer midplane decreases over time. The inset
  shows the relative length $L/L_0$ which remains nearly constant with a
  small oscillation. The inset and main panel have the same horizontal
  axis.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

@@

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in 
figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in figure~\ref{fig:PramChange}(e).
As shown in the supplementary material, these JP vesicles fluctuate/deform around a
steady shape of an octagon ($\lambda=1$ nm), a dimpled square ($\lambda=2$ nm),
a rounded diamond ($\lambda=3$ nm), and a rounded rectangle ($\lambda=4$ nm).

For $\lambda=1$ nm and $\lambda=2$ nm, multiple TG cells are inside the JP vesicle
as the inner leaflet of JPs move clockwise along the boundary faster than the outer leaflet.
For $\lambda=3$ nm and $\lambda=4$ nm, there is only one TG cell inside the JP vesicle
and the JPs in the bilayer tank-treading in the counter-clockwise direction
(Figure \ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculate the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
steady-state that is greatest for $\lambda = 4$ nm yet least for
$\lambda = 2$ nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
words, the flow pattern is non-monotonic in the cell size $\lambda$.
